---
title: "Daily Trends Scotland"
author: "Michael Kent"
date: "06/12/2020"
output: html_document
---
# To Do List

## List here all the charts to be drawn

* 4 nations daily 28 days since deaths / 10^5
* 4 nations weekly 28 days since  deaths / 10^5
* 4 nations daily certificate deaths / 10^5
* 4 nations weekly certificate deaths / 10^5
  * check MK PHS-ONS deaths data
* 4 nations positivity rates
* __4 nations testing rates__
* __Scotland deaths v NRO deaths__
* ___Scotland testing with event labels___
* Scotland 7 day cases by HB
* Scotland 7 day positive rates by HB
* Scotland 7 day cases positive rates by HB

## Other actions

- Check what other data is available on ONS/PHS and gov.scot sites.
- Create text for each chart/set of charts.
  - Do main picture and text with 'read more' sections.
  - Do an index page.
  - Transfer the code here to a script page with comments (lots!) 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(here)
library(janitor)
here()
```

# Reading in the data

```{r datainput}
# Standardised input - one dataset per spreadsheet/CSV

# New with new names
uk_d_28_day_testing <- read_excel(here("data","deaths_within_28_days_reported.xlsx"))
j_uk_d_28_day_testing = janitor::clean_names(uk_d_28_day_testing)
j_uk_d_28_day_testing_zoom <- j_uk_d_28_day_testing[-c(1:152), ]  #   Data from 1st Agust
# names(j_uk_d_28_day_testing)

# Reading data in  R-Table5-Testing.xlsx
sco_uk_testing <- read_excel(here("data","SCO-UK-Testing-data.xlsx"))

j_sco_uk_testing = janitor::clean_names(sco_uk_testing)
j_sco_uk_testing_zoom <- j_sco_uk_testing[-c(1:152), ]
#names(j_sco_uk_testing)
#cv_d_hb

```
# Extract Data
This extracts the data as a data frame.  Below we extract a line at a time.
```{r data_extract}
# First data frame is for Sco/UK testing comparison.
df_sc_uk_test <- data.frame(j_sco_uk_testing) %>%
  select(date_notified, uk_daily_tests_per_100_000_ma, sco_daily_tests_per_100_000_ma) %>%
  gather(key = "variable", value = "value",-date_notified)
head(df_sc_uk_test)

# Same data but from 1st August
df_sc_uk_test_zoom <- data.frame(j_sco_uk_testing_zoom) %>%
  select(date_notified, uk_daily_tests_per_100_000_ma, sco_daily_tests_per_100_000_ma) %>%
  gather(key = "variable", value = "value",-date_notified)
head(df_sc_uk_test_zoom)

# Daily positives from 1st August
df_sc_positive_zoom <- data.frame(j_sco_uk_testing_zoom) %>%
  select(date_notified, percent_daily_positive_ma) %>%
  gather(key = "variable", value = "value",-date_notified)
head(df_sc_positive_zoom)


# Second compares testing and case numbers.
df_sc_t5 <- data.frame(j_sco_uk_testing) %>%
  select(date_notified, daily_new_cases_scaled, daily_tests_7_day_ma) %>%
  gather(key = "variable", value = "value",-date_notified)
head(df_sc_t5)
# Same data but from 1st August
df_sc_t5_zoom <- data.frame(j_sco_uk_testing_zoom) %>%
  select(date_notified, daily_new_cases_scaled, daily_tests_7_day_ma) %>%
  gather(key = "variable", value = "value",-date_notified)
head(df_sc_t5)

```
```{r drawcharts}
# First, draw the Sco/UK testing
# Main
v_title="Testing rates for Scotland and all UK"
v_caption = "Source: UK and Scottish gov statistics as published 5th December 2020"
v_xlabel = "Date"
v_ylabel = "Tests per 100,000 population"
v_image_file_name = "2020_12_06 UK SC test compare.jpg"

ggplot(df_sc_uk_test, aes(x = date_notified, y = value)) + 
  geom_line(aes(color = variable),size=1 ) + theme_light() + 
  scale_color_manual(labels = c("Scotland", "Whole UK"),values = c("purple3", "steelblue3") ) +  
      labs(x = v_xlabel, 
          y = v_ylabel, 
          title = v_title,
          caption = v_caption,
          color = "") 
ggsave(here("figures", v_image_file_name), dpi = 180, width = 8, height = 6)

# Change image file name
v_image_file_name = "2020_12_06 UK SC test compare zoom.jpg"
ggplot(df_sc_uk_test_zoom, aes(x = date_notified, y = value)) + 
  geom_line(aes(color = variable),size=1 ) + theme_light() + 
  scale_color_manual(labels = c("Scotland", "Whole UK"),values = c("purple3", "steelblue3") ) +  
      labs(x = v_xlabel, 
          y = v_ylabel, 
          title = v_title,
          caption = v_caption,
          color = "") 
ggsave(here("figures", v_image_file_name), dpi = 180, width = 8, height = 6)

# Change image file name
v_image_file_name = "2020_12_06 percent daily positive MA.jpg"
ggplot(df_sc_positive_zoom, aes(x = date_notified, y = value)) + 
  geom_line(aes(color = variable),size=1 ) + theme_light() + 
      labs(x = v_xlabel, 
          y = v_ylabel, 
          title = v_title,
          caption = v_caption,
          color = "") 
ggsave(here("figures", v_image_file_name), dpi = 180, width = 8, height = 6)


# Then the Sco testing and case numbers
ggplot(df_sc_t5, aes(x = date_notified, y = value)) + 
  geom_line(aes(color = variable)) + theme_light() +
  facet_wrap(~ variable, ncol=1, scales = "free_y")

ggsave(here("figures", "test-case.jpg"), dpi = 180, width = 8, height = 6)

# Then the Sco testing and case numbers
ggplot(df_sc_t5_zoom, aes(x = date_notified, y = value)) + 
  geom_line(aes(color = variable)) + theme_light() +
  facet_wrap(~ variable, ncol=1, scales = "free_y")

ggsave(here("figures", "test-case_zoom.jpg"), dpi = 180, width = 8, height = 6)

```



<!-- ```{r drawlines} -->
<!-- sc_test_daycase <- ggplot(data = j_sco_uk_testing, aes(x = date_notified, y = daily_new_cases)) -->
<!-- sc_test_per_ma <- ggplot(data = j_sco_uk_testing, aes(x = date_notified, y =  daily_tests_per_100_000_ma )) -->
<!-- sc_test_daycase + geom_line() -->
<!-- sc_test_per_ma + geom_line() -->
<!-- ```   -->
  
  
  