---
title: "Daily Trends Scotland"
author: "Michael Kent"
date: "06/12/2020"
output: html_document
---
# To Do List

## List here all the charts to be drawn

* 4 nations daily 28 days since deaths / 10^5
* 4 nations weekly 28 days since  deaths / 10^5
* 4 nations daily certificate deaths / 10^5
* 4 nations weekly certificate deaths / 10^5
  * check MK PHS-ONS deaths data
* 4 nations positivity rates
* __4 nations testing rates__
* __Scotland deaths v NRO deaths__
* ___Scotland testing with event labels___
* Scotland 7 day cases by HB
* Scotland 7 day positive rates by HB
* Scotland 7 day cases positive rates by HB

## Other actions

- Check what other data is available on ONS/PHS and gov.scot sites.
- Create text for each chart/set of charts.
  - Do main picture and text with 'read more' sections.
  - Do an index page.
  - Transfer the code here to a script page with comments (lots!) 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(here)
library(janitor)
here()

# Create Datestamp
today <- format(Sys.Date(), format="%Y-%m-%d ") 
pubdate <- format(Sys.Date(), format="%d-%m-%Y ") 
v_caption = paste( "Source: UK and Scottish gov statistics as published ", pubdate, " © TTS", sep = "", collapse=NULL)

# LABELS
labels_28_day_deaths <- as_labeller(c(
                        'daily_new_cases_ma' = "Daily New Cases (7 day MA)",
                        'daily_tests_7_day_ma' = "Daily Tests Reported (7 day MA)"
))

labels_SCO_UK_Test <- as_labeller(c(`daily_new_cases_ma` = "Daily new cases (7 day MA)", `daily_tests_7_day_ma` = "Daily tests (7 day MA)"))


```

# Reading in the data

```{r datainput}
############ UPDATED ###############
# Standardised input - one dataset per spreadsheet/CSV
# Reading data for Scotland/UK testing
sco_uk_testing <- read_excel(here("data","d_SCO_UK_Testing.xlsx"))
j_sco_uk_testing = janitor::clean_names(sco_uk_testing)
j_sco_uk_testing_zoom <- j_sco_uk_testing[-c(1:152), ]
#names(j_sco_uk_testing)
#cv_d_hb





# New with new names
uk_d_28_day_testing <- read_excel(here("data","deaths_within_28_days_reported_v2.xlsx"))
j_uk_d_28_day_testing = janitor::clean_names(uk_d_28_day_testing)
j_uk_d_28_day_testing_zoom <- j_uk_d_28_day_testing[-c(1:211), ]  #   Data from 1st Agust
names(j_uk_d_28_day_testing)




```
# Extract Data
This extracts the data as a data frame.  Below we extract a line at a time.
```{r data_extract}

# Sco/UK testing comparison.
df_sc_uk_test <- data.frame(j_sco_uk_testing) %>%
  select(date_notified, uk_daily_tests_per_100_000_ma, sco_daily_tests_per_100_000_ma) %>%
  gather(key = "variable", value = "value",-date_notified)
#head(df_sc_uk_test)

# Sco/UK testing comparison from 1st August
df_sc_uk_test_zoom <- data.frame(j_sco_uk_testing_zoom) %>%
  select(date_notified, uk_daily_tests_per_100_000_ma, sco_daily_tests_per_100_000_ma) %>%
  gather(key = "variable", value = "value",-date_notified)
#head(df_sc_uk_test_zoom)

# Daily positives from 1st August
df_sc_positive_zoom <- data.frame(j_sco_uk_testing_zoom) %>%
  select(date_notified, percent_daily_positive_ma) %>%
  gather(key = "variable", value = "value",-date_notified)
#head(df_sc_positive_zoom)


# Second compares testing and case numbers.
df_sc_t5 <- data.frame(j_sco_uk_testing) %>%
  select(date_notified, daily_new_cases_ma, daily_tests_7_day_ma) %>%
  gather(key = "variable", value = "value",-date_notified)
#head(df_sc_t5)

# Same data but from 1st August
df_sc_t5_zoom <- data.frame(j_sco_uk_testing_zoom) %>%
  select(date_notified, daily_new_cases_ma, daily_tests_7_day_ma) %>%
  gather(key = "variable", value = "value",-date_notified)
#head(df_sc_t5_zoom)

# Same data but from 1st August
df_sc_t5_pos_zoom <- data.frame(j_sco_uk_testing_zoom) %>%
  select(date_notified, daily_new_cases_ma, daily_tests_7_day_ma) %>%
  gather(key = "variable", value = "value",-date_notified)
#head(df_sc_t5_pos_zoom)

# Now deaths within 28 days of a positive test
df_uk_d28_pos <- data.frame(j_uk_d_28_day_testing) %>%
  select(date_notified, england_7_day_ma_per_100_000:wales_7_day_ma_per_100_000) %>%
  gather(key = "variable", value = "value",-date_notified)
# head(df_uk_d28_pos)

# Same data but from 1st August
df_uk_d28_pos_zoom <- data.frame(j_uk_d_28_day_testing_zoom) %>%
  select(date_notified, england_7_day_ma_per_100_000:wales_7_day_ma_per_100_000) %>%
  gather(key = "variable", value = "value",-date_notified)
head(df_uk_d28_pos_zoom)

```
```{r drawcharts}
# Create Datestamp
today <- format(Sys.Date(), format="%Y-%m-%d ") 
pubdate <- format(Sys.Date(), format="%d/%m/%Y ") 
v_caption = paste( "Source: UK and Scottish gov statistics as published ", pubdate, " © Thetrue.scot", sep = "", collapse=NULL)
# LABELS
labels_SCO_UK_Test <- as_labeller(c(`daily_new_cases_ma` = "Daily new cases (7 day MA)", `daily_tests_7_day_ma` = "Daily tests (7 day MA)"))

p_geom <-geom_line(aes(color = variable),size=1 ) 

# First, draw the Sco/UK testing
v_title="Testing rates for Scotland and all UK"
v_xlabel = "Date"
v_ylabel = "Tests per 100,000 population"
v_image_file_name = paste(today, "UK SC test compare.jpg", sep = "", collapse=NULL)

ggplot(df_sc_uk_test, aes(x = date_notified, y = value)) + 
p_geom  + theme_light() + 
  #  geom_line(aes(color = variable),size=1 ) 
  scale_color_manual(labels = c("Scotland", "Whole UK"),values = c("purple3", "steelblue3") ) +  
      labs(x = v_xlabel, y = v_ylabel, title = v_title, caption = v_caption, color = "") +
ggsave(here("figures", v_image_file_name), dpi = 180, width = 8, height = 6)
#------------------------------------------------------------------------------------
# Change image file name
v_image_file_name = paste(today, "UK SC test compare zoom.jpg", sep = "", collapse=NULL)
ggplot(df_sc_uk_test_zoom, aes(x = date_notified, y = value)) + 
  geom_line(aes(color = variable),size=1 ) + theme_light() + 
  scale_color_manual(labels = c("Scotland", "Whole UK"),values = c("purple3", "steelblue3") ) +  
      labs(x = v_xlabel, y = v_ylabel, title = v_title, caption = v_caption, color = "") +
ggsave(here("figures", v_image_file_name), dpi = 180, width = 8, height = 6)
#------------------------------------------------------------------------------------
# Change image file name
v_image_file_name = paste(today, "Percent daily positive MA.jpg", sep = "", collapse=NULL)
ggplot(df_sc_positive_zoom, aes(x = date_notified, y = value)) + 
  geom_line(aes(color = variable),size=1 ) + theme_light() + 
      labs(x = v_xlabel, y = v_ylabel, title = v_title, caption = v_caption, color = "") +
ggsave(here("figures", v_image_file_name), dpi = 180, width = 8, height = 6)
#------------------------------------------------------------------------------------
v_title="Deaths within 28 days of positive death"
v_ylabel = "Weekly deaths per 100,000 population"
# Change image file name
v_image_file_name = paste(today, "Deaths within 28 days.jpg", sep = "", collapse=NULL)
ggplot(df_uk_d28_pos, aes(x = date_notified, y = value)) + 
  geom_line(aes(color = variable),size=1 ) + theme_light() + 
      labs(x = v_xlabel, y = v_ylabel, title = v_title, caption = v_caption, color = "") +
ggsave(here("figures", v_image_file_name), dpi = 180, width = 8, height = 6)
#------------------------------------------------------------------------------------
# Change image file name
v_image_file_name = paste(today, "Deaths within 28 days zoom.jpg", sep = "", collapse=NULL)
ggplot(df_uk_d28_pos_zoom, aes(x = date_notified, y = value)) + 
  geom_line(aes(color = variable),size=1 ) + theme_light() + 
      labs(x = v_xlabel, y = v_ylabel, title = v_title, caption = v_caption, color = "") +
ggsave(here("figures", v_image_file_name), dpi = 180, width = 8, height = 6)
#------------------------------------------------------------------------------------
##########################################################################
## TO DO
##         MUST CHANGE LABEL TEXT TO SUIT.
#
# v_image_file_name = paste(today, "UK SC test compare.jpg", sep = "", collapse=NULL)
###########################################################################
# Then the Sco testing and case numbers
# Change image file name
v_image_file_name = paste(today, "Testing v Case Numbers.jpg", sep = "", collapse=NULL)
ggplot(df_sc_t5, aes(x = date_notified, y = value)) + 
  geom_line(aes(color = variable)) + theme_light() +
  facet_wrap(~ variable, ncol=1, labeller = labels_SCO_UK_Test, scales = "free_y")
ggsave(here("figures", v_image_file_name), dpi = 180, width = 8, height = 6)

# Then the Sco testing and case numbers
# Change image file name
v_title="Daily New Cases and Tests"
v_xlabel = "Date"
v_ylabel = "Count"

v_image_file_name = paste(today, "Testing v Case Numbers zoom.jpg", sep = "", collapse=NULL)
ggplot(df_sc_t5, aes(x = date_notified, y = value)) + 
  geom_line(aes(color = variable)) + theme_light() +theme(legend.position = "none")+
      labs(x = v_xlabel, y = v_ylabel, title = v_title, caption = v_caption, color = "") +
  facet_wrap(~ variable , labeller = labels_28_day_deaths , ncol=1, scales = "free_y")

ggsave(here("figures", v_image_file_name), dpi = 180, width = 8, height = 6)

v_image_file_name = paste(today, "Testing v Case Numbers.jpg", sep = "", collapse=NULL)
ggplot(df_sc_t5_pos_zoom, aes(x = date_notified, y = value)) + 
  geom_line(aes(color = variable)) + theme_light() +theme(legend.position = "none")+
      labs(x = v_xlabel, y = v_ylabel, title = v_title, caption = v_caption, color = "") +
  facet_wrap(~ variable , labeller = labels_28_day_deaths, ncol=1, scales = "free_y")
ggsave(here("figures", v_image_file_name), dpi = 180, width = 8, height = 6)


```



<!-- ```{r drawlines} -->
<!-- sc_test_daycase <- ggplot(data = j_sco_uk_testing, aes(x = date_notified, y = daily_new_cases)) -->
<!-- sc_test_per_ma <- ggplot(data = j_sco_uk_testing, aes(x = date_notified, y =  daily_tests_per_100_000_ma )) -->
<!-- sc_test_daycase + geom_line() -->
<!-- sc_test_per_ma + geom_line() -->
<!-- ```   -->
  
  
  