---
title: "Daily Trends Scotland"
author: "Michael Kent"
date: "06/12/2020"
output: html_document
---
# Status
Changing this to have 
* Setup
* Data File Read
* Create Labellers
* Prepare data and then plot together

List of datasets and charts printed from them



# To Do List

## List here all the charts to be drawn

* 4 nations daily 28 days since deaths / 10^5
* 4 nations weekly 28 days since  deaths / 10^5
* 4 nations daily certificate deaths / 10^5
* 4 nations weekly certificate deaths / 10^5
  * check MK PHS-ONS deaths data
* 4 nations positivity rates
* __4 nations testing rates__
* __Scotland deaths v NRO deaths__
* ___Scotland testing with event labels___
* Scotland 7 day cases by HB
* Scotland 7 day positive rates by HB
* Scotland 7 day cases positive rates by HB

## Other actions

- Check what other data is available on ONS/PHS and gov.scot sites.
- Create text for each chart/set of charts.
  - Do main picture and text with 'read more' sections.
  - Do an index page.
  - Transfer the code here to a script page with comments (lots!) 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(here)
library(janitor)
here()

```

# Reading in the data

```{r datainput}
############ UPDATED ###############
# Standardised input - one dataset per spreadsheet/CSV
# Reading data for Scotland/UK testing
sco_uk_testing <- read_excel(here("data","d_SCO_UK_Testing.xlsx"))
j_sco_uk_testing = janitor::clean_names(sco_uk_testing)
j_sco_uk_testing_zoom <- j_sco_uk_testing[-c(1:152), ]
#names(j_sco_uk_testing)
###############################################################################
# New with new names
uk_d_28_day_testing <- read_excel(here("data","d_deaths_within_28_days_reported_v2.xlsx"))
j_uk_d_28_day_testing = janitor::clean_names(uk_d_28_day_testing)
j_uk_d_28_day_testing_zoom <- j_uk_d_28_day_testing[-c(1:211), ]  #   Data from 1st Agust
#names(j_uk_d_28_day_testing)
###############################################################################
# NEW 28 DAY IMPUT - COLUMNS

uk_d_28_day_testing2 <- read_excel(here("data","d_deaths_28_day_column.xlsx"))
j_uk_d_28_day_testing2 = janitor::clean_names(uk_d_28_day_testing2)
j_uk_d_28_day_testing_zoom2 <- j_uk_d_28_day_testing2[-c(1:211), ]  #   Data from 1st Agust
#names(j_uk_d_28_day_testing2)

df_uk_d28_pos <- data.frame(j_uk_d_28_day_testing2) %>%
  select(area_name,date,	new_deaths28days_by_death_date,	cum_deaths28days_by_death_date) %>%
  gather(key = "variable", value = "value",-area_name)
 head(df_uk_d28_pos)

###############################################################################
```
```{r break}

# Create Datestamp
today <- format(Sys.Date(), format="%Y-%m-%d ") 
filedate <- format(Sys.Date(), format="%Y-%m-%d") 
pubdate <- format(Sys.Date(), format="%d/%m/%Y ")
#save_folder <- paste("figures-",  today, sep = "", collapse=NULL)
v_caption = paste( "Chart © Thetrue.scot \n","Data Source: Scottish and UK government statistics as published ", pubdate,  sep = "", collapse=NULL)

#v_caption = paste( "Source: UK and Scottish gov statistics as published ", pubdate, " © Thetrue.scot", sep = "", collapse=NULL)


#getFP = file.path()
#save_folder= file.path("D:","TTS",filedate)
#file.path("D:","TTS",filedate)

# LABELS
labels_SCO_UK_Test <- as_labeller(c(
        `date_notified`  = "Date notified",
        `uk_daily_tests`  = "UK Daily Tests",
        `uk_daily_tests_per_100_000`  = "UK Daily Tests per 100,000",
        `uk_daily_tests_per_100_000_ma`  = "UK Daily Tests per 100,000 MA",
        `people_reported_negative`  = "People Reported Negative",
        `people_reported_positive`  = "People Reported Positive",
        `people_reported_total`  = "People Reported Total",
        `daily_new_cases`  = "Daily New Cases",
        `ratio_new_cases_to_people_newly_tested` = "ratio New cases to people newly tested",
        `nhs_reported_tests_daily`  = "NHS Reported Tests Daily",
        `nhs_reported_tests_cumulative`  = "NHS Reported Tests Cumulative",
        `uk_gov_reported_tests_daily`  = "UK Gov Reported Tests Daily",
        `uk_gov_reported_tests_cumulative`  = "UK Gov Reported Tests Cumulative",
        `scot_daily_tests`  = "Scot daily tests",
        `total_daily_positive_reported`  = "Total daily positive reported",
        `percent_daily_positive`  = "Percent Daily Positive",
        `people_with_first_test_7_days`  = "People with first test 7 days",
        `positive_cases_7_days`  = "Positive cases 7 days",
        `tests_reported_7_days`  = "Tests reported 7 days",
        `positive_tests_7_days`  = "Positive tests 7 days",
        `test_positivity_7_days`  = "Test positivity 7 days",
        `scot_daily_tests_per_1_000`  = "Scot daily tests per 1,000",
        `daily_new_cases_ma`  = "Daily New Cases MA",
        `percent_dnc`  = "Percent DNC",
        `daily_tests_7_day_ma`  = "daily tests 7 day MA",
        `sco_daily_tests_per_100_000`  = "Sco daily tests per 100,000",
        `sco_daily_tests_per_100_000_ma`  = "Sco Daily Tests per 100,000 MA",
        `percent_daily_positive_ma`  = "Percent Daily Positive MA",
        `new_cases_last_14_days`  = "New Cases last 14 days",
        `people_newly_tested` = "People Newly Tested",
        `people_newly_tested_ma` = "People Newly Tested MA"  ))

labels_28_day_deaths <- as_labeller(c(
        `daily_new_cases_ma` = "Daily New Cases (7 day MA)",
        `daily_tests_7_day_ma` = "Daily Tests Reported (7 day MA)"))

# LABELS
labels_HB_Data <- as_labeller(c(
        `nhs_ayrshire_arran`="NHS Ayrshire & Arran",
        `nhs_borders`="NHS Borders",
        `nhs_dumfries_galloway`="NHS Dumfries & Galloway",
        `nhs_fife`="NHS Fife",
        `nhs_forth_valley`="NHS Forth Valley",
        `nhs_grampian`="NHS Grampian",
        `nhs_greater_glasgow_clyde`="NHS Greater Glasgow & Clyde",
        `nhs_highland`="NHS Highland",
        `nhs_lanarkshire`="NHS Lanarkshire",
        `nhs_lothian`="NHS Lothian",
        `nhs_orkney`="NHS Orkney",
        `nhs_shetland`="NHS Shetland",
        `nhs_tayside`="NHS Tayside",
        `nhs_western_isles`="NHS Western Isles",
        `scotland`="Scotland"
                  ))
# Declare standard plot settings
p_geom <-geom_line(aes(color = variable),size=0.75 ) 


```
# Extract Data and Plot
This extracts the data as a data frame.  Below we extract a line at a time.
```{r SCO_UK_Testing}
###############################################################
## Scottish and UK testing data
# Prepare
v_title="Testing rates for Scotland and all UK"
v_xlabel = "Date"
v_ylabel = "Tests per 100,000 population"
v_image_file_name = paste(today, "UK SC test compare.jpg", sep = "", collapse=NULL)
v_image_file_name_zoom = paste(today, "UK SC test compare zoom.jpg", sep = "", collapse=NULL)

##-----------Sco/UK testing comparison ----------------------------------------
# All Data
df_sc_uk_test <- data.frame(j_sco_uk_testing) %>%
  select(date_notified, uk_daily_tests_per_100_000_ma, sco_daily_tests_per_100_000_ma) %>%
  gather(key = "variable", value = "value",-date_notified)
#head(df_sc_uk_test)

# from 1st August
# Sco/UK testing comparison from 1st August
df_sc_uk_test_zoom <- data.frame(j_sco_uk_testing_zoom) %>%
  select(date_notified, uk_daily_tests_per_100_000_ma, sco_daily_tests_per_100_000_ma) %>%
  gather(key = "variable", value = "value",-date_notified)
#head(df_sc_uk_test_zoom)

#PLOTS
ggplot(df_sc_uk_test, aes(x = date_notified, y = value)) + 
p_geom  + theme_light() + 
  scale_color_manual(labels = c("Scotland", "Whole UK"),values = c("purple3", "steelblue3") ) +  # OK #
      labs(x = v_xlabel, y = v_ylabel, title = v_title, caption = v_caption, color = "") +
ggsave(here("figures", v_image_file_name), dpi = 180, width = 8, height = 6)

ggplot(df_sc_uk_test_zoom, aes(x = date_notified, y = value)) + 
  p_geom  + theme_light() + 
  scale_color_manual(labels = c("Scotland", "Whole UK"),values = c("purple3", "steelblue3") ) +  # OK #
      labs(x = v_xlabel, y = v_ylabel, title = v_title, caption = v_caption, color = "") +
ggsave(here("figures", v_image_file_name_zoom), dpi = 180, width = 8, height = 6)

```
```{r SCO_Daily_Positive }
#---------- Daily Positive Data ------------------------------------------------
# Prepare
v_title="Positive test rates for Scotland"
v_xlabel = "Date"
v_ylabel = "Percentage tests positive"
v_image_file_name = paste(today, "UK SC test compare.jpg", sep = "", collapse=NULL)
v_image_file_name_zoom = paste(today, "UK SC test compare zoom.jpg", sep = "", collapse=NULL)

# Daily positives all data
df_sc_positive <- data.frame(j_sco_uk_testing) %>%
  select(date_notified, percent_daily_positive_ma) %>%
  gather(key = "variable", value = "value",-date_notified)
#head(df_sc_positive)

# Daily positives from 1st August
df_sc_positive_zoom <- data.frame(j_sco_uk_testing_zoom) %>%
  select(date_notified, percent_daily_positive_ma) %>%
  gather(key = "variable", value = "value",-date_notified)
#head(df_sc_positive_zoom)

# Change image file name
v_image_file_name = paste(today, "Percent daily positive MA.jpg", sep = "", collapse=NULL)
ggplot(df_sc_positive, aes(x = date_notified, y = value)) + 
  p_geom  + theme_light() + theme(legend.position = "none")+
  labs(x = v_xlabel, y = v_ylabel, title = v_title, caption = v_caption, color = "") +
ggsave(here("figures", v_image_file_name), dpi = 180, width = 8, height = 6)

# Change image file name
v_image_file_name = paste(today, "Percent daily positive MA zoom.jpg", sep = "", collapse=NULL)
ggplot(df_sc_positive_zoom, aes(x = date_notified, y = value)) + 
  p_geom  + theme_light() + theme(legend.position = "none")+
  labs(x = v_xlabel, y = v_ylabel, title = v_title, caption = v_caption, color = "") +
ggsave(here("figures", v_image_file_name), dpi = 180, width = 8, height = 6)

```
```{r SCO_Tests_New_Cases}
#-----------------Compare Tests and new cases-----------------------------------
# Second compares testing and case numbers.
df_sc_t5 <- data.frame(j_sco_uk_testing) %>%
  select(date_notified, daily_new_cases_ma, daily_tests_7_day_ma) %>%
  gather(key = "variable", value = "value",-date_notified)
#head(df_sc_t5)

# Same data but from 1st August
df_sc_t5_zoom <- data.frame(j_sco_uk_testing_zoom) %>%
  select(date_notified, daily_new_cases_ma, daily_tests_7_day_ma) %>%
  gather(key = "variable", value = "value",-date_notified)
#head(df_sc_t5_zoom)

# Same data but from 1st August
df_sc_t5_pos_zoom <- data.frame(j_sco_uk_testing_zoom) %>%
  select(date_notified, daily_new_cases_ma, daily_tests_7_day_ma) %>%
  gather(key = "variable", value = "value",-date_notified)
#head(df_sc_t5_pos_zoom)
# Then the Sco testing and case numbers
# Change image file name
v_image_file_name = paste(today, "Testing v Case Numbers.jpg", sep = "", collapse=NULL)
ggplot(df_sc_t5, aes(x = date_notified, y = value)) + 
  p_geom + theme_light() +theme(legend.position = "none")+ 
    facet_wrap(~ variable, ncol=1, labeller = labels_SCO_UK_Test, scales = "free_y")
ggsave(here("figures", v_image_file_name), dpi = 180, width = 8, height = 6)

# Then the Sco testing and case numbers
# Change image file name
v_title="Daily New Cases and Tests"
v_xlabel = "Date"
v_ylabel = "Count"
# Testing v positive tests
v_image_file_name = paste(today, "Testing v New Cases.jpg", sep = "", collapse=NULL)
ggplot(df_sc_t5, aes(x = date_notified, y = value)) + 
    p_geom + theme_light() +theme(legend.position = "none")+
      labs(x = v_xlabel, y = v_ylabel, title = v_title, caption = v_caption, color = "") +
  facet_wrap(~ variable , labeller = labels_28_day_deaths , ncol=1, scales = "free_y")

ggsave(here("figures", v_image_file_name), dpi = 180, width = 8, height = 6)

v_image_file_name = paste(today, "Testing v New Cases zooms.jpg", sep = "", collapse=NULL)
ggplot(df_sc_t5_pos_zoom, aes(x = date_notified, y = value)) + 
    p_geom + theme_light() +theme(legend.position = "none")+
      labs(x = v_xlabel, y = v_ylabel, title = v_title, caption = v_caption, color = "") +
  facet_wrap(~ variable , labeller = labels_28_day_deaths, ncol=1, scales = "free_y")
ggsave(here("figures", v_image_file_name), dpi = 180, width = 8, height = 6)

```
```{r SCO_Active_Cases_14_days}
##---------Active Cases - Positive within 14 days ------------------------------
#  Active Cases
# Daily Active cases (14)
df_sc_new_cases <- data.frame(j_sco_uk_testing) %>%
  select(date_notified, new_cases_last_14_days) %>%
  gather(key = "variable", value = "value",-date_notified)
#head(df_sc_new_cases)

# Daily Active cases (14)
df_sc_new_cases_zoom <- data.frame(j_sco_uk_testing_zoom) %>%
  select(date_notified, new_cases_last_14_days) %>%
  gather(key = "variable", value = "value",-date_notified)
#head(df_sc_new_cases_zoom)

#------------------------------------------------------------------------------------
#  Active Cases
v_title="Known Active Cases (positive in last 14 days)"
v_xlabel = "Date"
v_ylabel = "Number of cases"
v_image_file_name = paste(today, "Active Cases Scotland.jpg", sep = "", collapse=NULL)
ggplot(df_sc_new_cases, aes(x = date_notified, y = value)) + 
p_geom  + theme_light() + 
  #  geom_line(aes(color = variable),size=1 ) 
  scale_color_manual(labels = c("Active Cases"),values = c("purple3") ) +  
      labs(x = v_xlabel, y = v_ylabel, title = v_title, caption = v_caption, color = "") +
ggsave(here("figures", v_image_file_name), dpi = 180, width = 8, height = 6)
#------------------------------------------------------------------------------------
# Change image file name
v_image_file_name = paste(today, "Active Cases Scotland zoom.jpg", sep = "", collapse=NULL)
ggplot(df_sc_new_cases_zoom, aes(x = date_notified, y = value)) + 
p_geom  + theme_light() + 
  #  geom_line(aes(color = variable),size=1 ) 
  scale_color_manual(labels = c("Active Cases"),values = c("purple3") ) +  
      labs(x = v_xlabel, y = v_ylabel, title = v_title, caption = v_caption, color = "") +
ggsave(here("figures", v_image_file_name), dpi = 180, width = 8, height = 6)

```
```{r SCO_Active_Cases_14_days}
##---------Number of people newly tested ------------------------------
# Newly Tested MA
df_sc_new_tests <- data.frame(j_sco_uk_testing) %>%
  select(date_notified, people_newly_tested_ma) %>%
  gather(key = "variable", value = "value",-date_notified)
#head(df_sc_new_cases)

# Newly Tested MA
df_sc_new_tests_zoom <- data.frame(j_sco_uk_testing_zoom) %>%
  select(date_notified, people_newly_tested_ma) %>%
  gather(key = "variable", value = "value",-date_notified)
#head(df_sc_new_cases_zoom)

#------------------------------------------------------------------------------------
# Newly Tested MA
v_title="People Newly Tested"
v_xlabel = "Date"
v_ylabel = "Number of cases"
v_image_file_name = paste(today, "People Newly Tested.jpg", sep = "", collapse=NULL)
ggplot(df_sc_new_tests, aes(x = date_notified, y = value)) + 
p_geom  + theme_light() + 
  #  geom_line(aes(color = variable),size=1 ) 
  scale_color_manual(labels = c("Active Cases"),values = c("purple3") ) +  
      labs(x = v_xlabel, y = v_ylabel, title = v_title, caption = v_caption, color = "") +
ggsave(here("figures", v_image_file_name), dpi = 180, width = 8, height = 6)
#------------------------------------------------------------------------------------
# Change image file name
v_image_file_name = paste(today, "People Newly Tested zoom.jpg", sep = "", collapse=NULL)
ggplot(df_sc_new_tests_zoom, aes(x = date_notified, y = value)) + 
p_geom  + theme_light() + 
  #  geom_line(aes(color = variable),size=1 ) 
  scale_color_manual(labels = c("Active Cases"),values = c("purple3") ) +  
      labs(x = v_xlabel, y = v_ylabel, title = v_title, caption = v_caption, color = "") +
ggsave(here("figures", v_image_file_name), dpi = 180, width = 8, height = 6)

```

```{r UK_Deaths_28_Days}

#------- Deaths within 28 days of positive test (UK)----------------------------
## UK 28 days death data
#
# Now deaths within 28 days of a positive test
df_uk_d28_pos <- data.frame(j_uk_d_28_day_testing) %>%
  select(date_notified, england_7_day_ma_per_100_000:wales_7_day_ma_per_100_000) %>%
  gather(key = "variable", value = "value",-date_notified)
# head(df_uk_d28_pos)

# Same data but from 1st August
df_uk_d28_pos_zoom <- data.frame(j_uk_d_28_day_testing_zoom) %>%
  select(date_notified, england_7_day_ma_per_100_000:wales_7_day_ma_per_100_000) %>%
  gather(key = "variable", value = "value",-date_notified)
head(df_uk_d28_pos_zoom)

v_title="Deaths within 28 days of positive death"
v_ylabel = "Weekly deaths per 100,000 population"
# Change image file name
v_image_file_name = paste(today, "Deaths within 28 days.jpg", sep = "", collapse=NULL)
ggplot(df_uk_d28_pos, aes(x = date_notified, y = value)) + 
  p_geom  + theme_light() + 
  labs(x = v_xlabel, y = v_ylabel, title = v_title, caption = v_caption, color = "") +
ggsave(here("figures", v_image_file_name), dpi = 180, width = 8, height = 6)

# Change image file name
v_image_file_name = paste(today, "Deaths within 28 days zoom.jpg", sep = "", collapse=NULL)
ggplot(df_uk_d28_pos_zoom, aes(x = date_notified, y = value)) + 
  p_geom  + theme_light() + 
  labs(x = v_xlabel, y = v_ylabel, title = v_title, caption = v_caption, color = "") +
ggsave(here("figures", v_image_file_name), dpi = 180, width = 8, height = 6)

#------------------------------------------------------------------------------------

```
```{r drawcharts}

#------------------------------------------------------------------------------------
##########################################################################
## TO DO

#------------------------------------------------------------------------------------
# Testing v Positive Tests v Active Cases
v_image_file_name = paste(today, "Testing v New Cases.jpg", sep = "", collapse=NULL)
ggplot(df_sc_t5, aes(x = date_notified, y = value)) + 
    p_geom + theme_light() +theme(legend.position = "none")+
      labs(x = v_xlabel, y = v_ylabel, title = v_title, caption = v_caption, color = "") +
  facet_wrap(~ variable , labeller = labels_28_day_deaths , ncol=1, scales = "free_y")

ggsave(here("figures", v_image_file_name), dpi = 180, width = 8, height = 6)

#v_image_file_name = paste(today, "Testing v New Cases zooms.jpg", sep = "", collapse=NULL)
#ggplot(df_sc_t5_pos_zoom, aes(x = date_notified, y = value)) + 
#    p_geom + theme_light() +theme(legend.position = "none")+
#      labs(x = v_xlabel, y = v_ylabel, title = v_title, caption = v_caption, color = "") +
#  facet_wrap(~ variable , labeller = labels_28_day_deaths, ncol=1, scales = "free_y")
#ggsave(here("figures", v_image_file_name), dpi = 180, width = 8, height = 6)




```



<!-- ```{r drawlines} -->
<!-- sc_test_daycase <- ggplot(data = j_sco_uk_testing, aes(x = date_notified, y = daily_new_cases)) -->
<!-- sc_test_per_ma <- ggplot(data = j_sco_uk_testing, aes(x = date_notified, y =  daily_tests_per_100_000_ma )) -->
<!-- sc_test_daycase + geom_line() -->
<!-- sc_test_per_ma + geom_line() -->
<!-- ```   -->
  
  
  