---
title: "Cases by Health Board"
author: "Michael Kent"
date: "05/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(here)
library(janitor)
here()
```

# Reading in the data
This section is set up to read the processed numbers and display them as graphs.  

* Initial setup reads the cases by health board data from an Excel spreadsheet.
* Extracts the data into a data frame
* Draws the graph.

## Next section will
* Read all testing data and put each 'set' into a variabe which will allow 'mix and match.
* Produce the various 'slices' of the data that I want.
* Export the graphs for the TTS website.

## Data Processing
Will learn and implement methods of processing rawer data so I do less with Excel.

```{r datainput}
# Reading data in
#ca_np <- read_csv(here("data", "ca_np.csv"))
cv_d_hb <- read_excel(here("data","tests_by_hb.xlsx"))
j_cv_d_hb = janitor::clean_names(cv_d_hb)
names(j_cv_d_hb)
#cv_d_hb

```
# Extract Data
```{r data_extract}
df <- data.frame(j_cv_d_hb) %>%
  select(date_notified, nhs_ayrshire_arran:nhs_western_isles) %>%
  gather(key = "variable", value = "value",-date_notified)
head(df)
#df
```
```{r drawcharts}
ggplot(df, aes(x = date_notified, y = value)) + 
  geom_line(aes(color = variable)) + theme_light() # +facet_wrap(~ variable)
#  scale_color_manual(values = c("darkred", "steelblue"))
ggsave(here("figures", "np_graph.jpg"), dpi = 180, width = 20, height = 20)
```
